### 2017-01-06 doc/manuscript.Rmd
Included MonthsFromBaseline median, IQR in results
Clarified that most participants had a 6yr visit
Added handling of diabetes cases in methods

Generalized estimating equation (GEE) models [@Zeger1986a] were used in the
primary analysis to determine the longitudinal associations between the outcome
variables and the predictor variables. Given the longitudinal design, an
auto-regressive of order 1 (AR1) working correlation matrix was chosen for the GEE
models as it had the best model fit when assessed using quasi-likelihood
information criteria (QIC), though other matrices (eg. exchangeable)
had similar fit (data not shown). GEE is well suited to longitudinal cohort 
studies given it's capacity to handle missed visits. The predictor variables and
continuous covariates were scaled (mean-centered and standardized). The TAGFA,
total NEFA, sex, ethnicity, and baseline age were classified as 
*time-independent* (held constant) as they were measured only at the baseline 
visit or do not change throughout the study, while the outcome variables and 
remaining covariates were set as *time-dependent*. No imputation was conducted 
on missing values.

@@

While GEE accounts for the longitudinal design of the data, this approach is 
limited in that it cannot analyze the inherent multivariate nature of the 
composition of the TAGFA fraction. To confirm the GEE results in a multivariate 
environment (all TAGFA), partial least squares regression (PLS) {{citation}} was
used to identify the patterns of TAGFA composition against insulin sensitivity
and beta-cell function. 
For more detailed explanation of GEE and PLS, please see
the {{supplemental}} Methods.

@@

`r tab_basic` shows some basic characteristics of the PROMISE cohort. There were
`r female$npct` females and `r euro$npct` who had European-ancestry, with a mean
age in years of `r aide::ave_sd(ds0yr$Age)` and a mean BMI
of `r aide::ave_sd(ds0yr$BMI)`. Given the eligibility criteria, the majority of
participants (`r fhd$npct`) had a family history of diabetes.
Between the baseline visit and the 6-year visit in this sample, insulin
sensitivity and beta-cell function measures had a significant median decline
between `r outcome_chg$chg` (p`r outcome_chg$p`; n=`r outcome_chg$n`). There 
were `r dys$dm` and `r dys$pre` incident cases of diabetes and
pre-diabetes (IFG and IGT), respectively. {{ confirm this is incidence }}

>>>>

Generalized estimating equation (GEE) models [@Zeger1986a] were used in the
primary analysis to determine the longitudinal associations between the outcome
variables and the predictor variables. Given the longitudinal design, an
auto-regressive of order 1 (AR1) working correlation matrix was chosen for the GEE
models as it had the best model fit when assessed using quasi-likelihood
information criteria (QIC), though other matrices (eg. exchangeable)
had similar fit (data not shown). GEE is well suited to longitudinal cohort 
studies given it's capacity to handle missed visits. The predictor variables and
continuous covariates were scaled (mean-centered and standardized). The TAGFA,
total NEFA, sex, ethnicity, and baseline age were classified as 
*time-independent* (held constant) as they were measured only at the baseline 
visit or do not change throughout the study, while the outcome variables and 
remaining covariates were set as *time-dependent*. No imputation was conducted 
on missing values. Given how the samples for TAGFA measurement were determined
and how the outcome variables are calculated, cases of diabetes at baseline and
followup were not included in the GEE modeling.

@@

While GEE accounts for the longitudinal design of the data, this approach is 
limited in that it cannot analyze the inherent multivariate nature of the 
composition of the TAGFA fraction. To confirm the GEE results in a multivariate 
environment (all TAGFA), partial least squares regression (PLS) {{citation}} was
used to identify the patterns of TAGFA composition against insulin sensitivity
and beta-cell function. No prevalent diabetes cases were included in the PLS
analysis. For more detailed explanation of GEE and PLS, please see the
{{supplemental}} Methods.

@@

`r tab_basic` shows some basic characteristics of the PROMISE cohort. The mean 
follow-up time was `r calc_followup_time()`, where `r calc_pct_full_visits()`%
of participants attended all three visits. There were
`r female$npct` females and `r euro$npct` who had European-ancestry, with a mean
age in years of `r aide::ave_sd(ds0yr$Age)` and a mean BMI
of `r aide::ave_sd(ds0yr$BMI)`. Given the eligibility criteria, the majority of
participants (`r fhd$npct`) had a family history of diabetes.
Between the baseline visit and the 6-year visit in this sample, insulin
sensitivity and beta-cell function measures had a significant median decline
between `r outcome_chg$chg` (p`r outcome_chg$p`; n=`r outcome_chg$n`). There 
were `r dys$dm` and `r dys$pre` incident cases of diabetes and
pre-diabetes (IFG and IGT), respectively. {{ confirm this is incidence }}
